Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-b} & 
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-d} \\ 
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1'$ and $R_2'$ &
        \hspace{-4mm} (c) $R_1'$, $R_2'$, $H$, and $V$ &
        \hspace{-4mm} (d) $R_1^*$, $R_2^* = \emptyset$, and $H$ 
    \end{tabular}
    \figcapup 
    \caption{Finding H-V $k$-SJ result tuples of type 1 ($k = 4$)} 
    \label{fig:hv:type1:ex}
    \figcapdown 
\end{figure*}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} &
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} & 
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1} &
        \hspace{-3mm}
        \includegraphics[height=43mm]{./artwork/alg-ex1}
    \end{tabular}
\end{figure*}

@@

@@

@@

>>>>

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-b} & 
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-d} \\ 
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1'$ and $R_2'$ &
        \hspace{-4mm} (c) $R_1'$, $R_2'$, $H$, and $V$ &
        \hspace{-4mm} (d) $R_1^*$, $R_2^*$ ($= \emptyset$), and $H$
    \end{tabular}
    \figcapup 
    \caption{Finding H-V $k$-SJ result tuples of type 1 ($k = 4$)} 
    \label{fig:hv:type1:ex}
    \figcapdown 
\end{figure*}

@@

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-b} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex2-d} \\
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1$, $H'$, and $V$ &
        \hspace{-4mm} (c) $R_1$, $R_2$, $H'$, and $V$ &
        \hspace{-4mm} (d) $R_2$ and $H^*$
    \end{tabular}
    \figcapup
    \caption{Finding H-V $k$-SJ result tuples of type 2 ($k = 4$)}
    \label{fig:hv:type2:ex}
    \figcapdown
\end{figure*}

@@

\extraspacing {\underline{\em Example 5.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_2)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \qed

@@

\noindent {\underline{\em Example 5.2.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_2)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \qed

@@

\input{appB.tex}
